---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# baltagi

<!-- badges: start -->
<!-- badges: end -->

## About

'Econometric Analysis of Panel Data' (ISBN 978-3-030-53952-8)
provides up-to-date coverage of basic panel data techniques, illustrated
with real economic applications and datasets. However, importing the
original data from the book into R is not straightforward because
some of the datasets are available in Microsoft Word format. I provide the
datasets in tidy format, expecting that this will allow students to focus on
the econometric techniques rather than on data wrangling.

## Installation

You can install the development version of baltagi like so:

``` r
remotes::install_github("pachadotdev/baltagi")
```

## Example

Baltagi, Song and Jung (2001) investigated the productivity of public capital in
each US state's private output, which is discussed in section 9.6.1 of the book
(Empirical Example: Nested States Public Capital Productivity).

The original dataset is in Microsoft Word format (DOCX). To read it, you would
need to copy it in Notepad, save as CSV , and then import it into R to find that
there are data wrangling steps involved to make it usable. Alternatively, you
can read the DOCX file directly in R with the `readtext` package and then
proceed to the data wrangling.

`baltagi` saves all those steps and you can jump directly to the econometric
analysis.

```{r example}
library(baltagi)
library(plm)

fit <- plm(
  log(gsp) ~ log(priv_cap) + log(hwy) + log(water) + log(util) + log(emp) +
    unemp,
  data = produc,
  index = c("st_abb", "year")
)

summary(fit)
```
